\documentclass[12pt]{article}
\usepackage[british]{babel}
\usepackage{amsmath, amssymb, amsfonts, amscd}
\usepackage{latexsym}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{etoolbox}

\topmargin -15mm
\textwidth 170mm
\textheight 224mm
\oddsidemargin -7mm
\evensidemargin -7mm
\sloppy

\synctex=1

\newtoggle{full}
\togglefalse{full}

% pdflatex -jobname=AGcv AGcv_short.tex
% will write the output to AGcv.pdf

\begin{document}

\centerline{\large \bf Curriculum Vitae}
\vskip5mm
\centerline{\Large \bfseries A\normalsize LEX \Large G\normalsize AVRYUSHKIN}
\vskip5mm
\centerline{19\textsuperscript{th} April 2018}
\vskip5mm

\centerline{\bf Contacts}
\begin{tabbing}
00000000000000000	\= Department of Computer Science	\kill
Address:		\> Department of Computer Science\\
			\> University of Otago\\
			\> Owheo Building, Room 244\\
			\> 133 Union St E\\
			\> Dunedin 9016, New Zealand\\
Homepage:		\> \href{http://lab.gavruskin.com}{http://lab.gavruskin.com}\\
Email:			\> \href{mailto:alex@gavruskin.com}{alex@gavruskin.com}
\end{tabbing}

\centerline{\bf Education}
\begin{tabbing}
00000	\= 0000000000000000000000	\=	\kill
2009	\> Ph.\,D.\ in Mathematics	\> from Sobolev Institute of Mathematics, Novosibirsk\\
2006	\> M.\,S.\ in Mathematics	\> from Novosibirsk State University (with First Class Honours)\\
2004	\> B.\,S.\ in Mathematics	\> from Novosibirsk State University (with First Class Honours)
\end{tabbing}

\centerline{\bf Professional Activity}
\begin{tabbing}
September	\=2009\=--\=November	\=00000	\= 000000000000000000		\= \kill
February	\>2018\>--\>present	\>	\> Senior Lecturer		\> University of Otago (NZ)\\
		\>    \>  \>		\>	\>				\> Department of Computer Science\\
August		\>2016\>--\>January	\>2018	\> Research Fellow		\> ETH Zurich (CH)\\
		\>    \>  \>		\>	\>				\> Dept Biosystems Science and Engineering\\
\iftoggle{full}{
August		\>2016\>--\>January	\>2018	\> Member			\> SIB Swiss Institute of Bioinformatics (CH)\\
		\>    \>  \>		\>	\>				\> Computational Biology Group\\
}{}
February	\>2012\>--\>July	\>2016	\> Research Fellow		\> The University of Auckland (NZ)\\
		\>    \>  \>		\>	\>				\> Department of Computer Science\\
\iftoggle{full}{
February	\>2015\>--\>February	\>2016	\> Affiliate			\> Fred Hutchinson Cancer Research Centre (US)\\
		\>    \>  \>		\>	\>				\> Computational Biology Program\\
January		\>2016\>--\>June	\>2016	\> Short-term visitor		\> Simons Institute for the Theory of Computing\\
		\>    \>  \>		\>	\>				\> UC Berkeley (US)\\
August		\>2013\>--\>July	\>2014	\> Lecturer	 		\> Auckland University of Technology (NZ)\\
		\>    \>  \>		\>	\>				\> School of Computer and Mathematical Sciences\\
November	\>2012\>--\>June	\>2013	\> Research Visitor		\> National University of Singapore\\
		\>    \>  \>		\>	\>				\> School of Computing\\
September	\>2009\>--\>December	\>2014	\> Senior Lecturer		\> Irkutsk State University (RF)\\
		\>    \>  \>		\>	\>				\> Institute of Mathematics, Economics, and\\
		\>    \>  \>            \>      \>                              \> Computer Science\\
\end{tabbing}
}{
September	\>2009\>--\>December	\>2014	\> Senior Lecturer		\> Irkutsk State University (RF)\\
		\>    \>  \>		\>	\>				\> Institute of Mathematics, Economics, and\\
		\>    \>  \>		\>	\>				\> Computer Science
\end{tabbing}
}


\centerline{\bf Awards}
\begin{tabbing}
000000	\=	\kill
2017	\> Rutherford Discovery Fellowship (five years, Royal Society of New Zealand)\\
2011	\> Dr of Science Scholarship (three years, Government of Russia)\\
2009	\> Siberian Fund for Algebra and Logic Award (2005--2009)\\
2008	\> Award for excellence in teaching (at ACM-ICPC North-Eastern European Regional Contest)\\
2007	\> Siberian Mathematical Journal Award (from Sobolev Institute of Mathematics)\\
2006	\> Best Student Scientific Work Award (from Novosibirsk State University)\\
2005	\> Maltsev Award (from Novosibirsk State University)\iftoggle{full}{\\
2000	\> Gold Medal (from the Government of Russia, Novokuznetsk High School \#32)
}{}
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Publications}
}{
\newpage
\centerline{\bf Recent publications}
}
\begin{itemize}
\item A.\,Gould, V.\,Zhang, L.\,Lamberti, E.\,Jones, B.\,Obadia, A.\,Gavryushkin, J.\,Carlson, N.\,Beerenwinkel, W.\,Ludington.
	High-dimensional microbiome interactions shape host fitness.
	{\em bioRxiv,} DOI 10.1101/232959, 2018.
\item C.\,Lienkaemper, L.\,Lamberti, J.\,Drain, N.\,Beerenwinkel, and A.\,Gavryushkin.
	The geometry of partial fitness orders and an efficient method for detecting genetic interactions.
	{\em Journal of Mathematical Biology,} DOI: 10.1007/s00285-018-1237-7, 2018
\item K.\,Crona$^*$, A.\,Gavryushkin$^*$, D.\,Greene$^*$, and N.\,Beerenwinkel.
	Inferring genetic interactions from comparative fitness data.
	{\em eLife,} 2017;6:e28629, DOI: 10.7554/eLife.28629, 2017.
	$^*$Equal contribution, alphabetic order.
\item A.\,Gavryushkin, C.\,Whidden, and F.\,Matsen IV.
	The combinatorics of discrete time-trees: theory and open problems.
	{\em Journal of Mathematical Biology,} 76, 5, 1101--1121, 2017.
\item C.\,Zeidler, G.\,Weber, A.\,Gavryushkin, and C.\,Lutteroth.
	Tiling algebra for constraint-based layout editing.
	{\em Journal of Logical and Algebraic Methods in Programming,} Vol.\,89, 67--94, 2017.
\item A.\,Gavryushkin and A.\,Drummond.
	The space of ultrametric phylogenetic trees.
	{\em Journal of Theoretical Biology,} Vol.\,403, 197--208, 2016.
\item P.\,Gavryushkin, A.\,Behtenova, Z.\,Popov, V.\,Bakakin, A.\,Likhacheva, K.\,Litasov, and A.\,Gavryushkin.
	Toward analysis of structural changes common for alkaline carbonates and binary compounds: prediction of high-pressure structures of Li2CO3, Na2CO3, and K2CO3.
	{\em Crystal Growth \& Design,} 16, 10, 5612--5617, 2016.
\item P.\,Gavryushkin, Z.\,Popov, K.\,Litasov, A.\,Belonoshko, and A.\,Gavryushkin.
	Stability of B2-type FeS at Earth's inner core pressures.
	{\em Geophysical Research Letters,} 43, 16, 8435--8440, 2016.
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamic algorithms for multimachine interval scheduling through analysis of idle intervals.
	{\em Algorithmica,} DOI 10.1007/s00453-016-0148-5, 2016.
\item T.\,Stadler, T.\,Vaughan, A.\,Gavryushkin, S.\,Guindon, D.\,K\"uhnert, G.E.\,Leventhal, and A.\,Drummond.
	How well can the exponential-growth coalescent approximate constant-rate birth-death population dynamics?
	{\em Proceedings of the Royal Society B: Biological Sciences,} 282, 1806, 2015.
\item P.\,Gavryushkin, Z.\,Popov, K.\,Litasov, and A.\,Gavryushkin.
	Unbiased crystal structure prediction of $\mathrm{NiSi}$ under high pressure.
	{\em Journal of Applied Crystallography,} 48, 3, 906--908, 2015.
\item A.\,Gavryushkin, B.\,Khoussainov, and F.\,Stephan.
	Reducibilities among equivalence relations induced by recursively enumerable structures.
	{\em Theoretical Computer Science,} Vol.\,612, 137--152, 2015.
\item A.\,Gavryushkin.
	Decidable models of small theories.
	{\em Lobachevskii Journal of Mathematics,} 36, 4, 446--449, 2015.
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamic algorithms for monotonic interval scheduling problem.
	{\em Theoretical Computer Science,} Vol.\,562, 227--242, 2014.
\item A.\,Gavryushkin and A.\,Nies.
	Universality for left-computably enumerable metric spaces.
	{\em Lobachevskii Journal of Mathematics,} 35, 4, 292--294, 2014.
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamic interval scheduling for multiple machines.
	{\em ISAAC 2014, Springer LNCS,} Vol.\,8889, 235--246, 2014.
\item A.\,Gavryushkin, S.\,Jain, B.\,Khoussainov, and F.\,Stephan.
	Graphs realised by r.\,e.\ equivalence relations.
	{\em Annals of Pure and Applied Logic,} 165, 7, 1263--1290, 2014.
\iftoggle{full}{
\item A.\,Gavryushkin, B.\,Khoussainov, M.\,Kokho, and J.\,Liu.
	Dynamising interval scheduling: the monotonic case.
	{\em IWOCA 2013, Springer LNCS,} Vol.\,8288, 178--189, 2013.
\item A.\,Gavryushkin and B.\,Khoussainov.
	On decidable and computable models of theories.
	{\em CiE 2013, Springer LNCS,} Vol.\,7921, 200--209, 2013.
\item A.\,Gavryushkin.
	On constructive models of theories with linear Rudin-Keisler ordering.
	{\em Journal of Logic and Computation,} 22, 4, 793--805, 2012.
\item A.\,Gavryushkin.
	Computable models of Ehrenfeucht theories.
	{\em CRM Documents}, Centre de Recerca Matem\`atica, Bellaterra (Barcelona), Vol.\,11, 67--77, 2012.
\item A.\,Gavryushkin.
	A new spectrum of computable models.
	{\em Bulletin of ISU.
	Series: mathematics,} 4, 4, 7--20, 2010.
\item A.\,Gavryushkin.
	Computable limit models.
	{\em Programs, Proofs, Processes---CiE,} 188--193, 2010.
\item A.\,Gavryushkin.
	Computable limit models for Ehrenfeucht theories.
	{\em Bulletin of ISU.
	Series: mathematics,} 3, 2, 56--61, 2009.
\item A.\,Gavryushkin.
	Computable models of theories with linear Rudin-Keisler ordering.
	{\em Bulletin of NSU.
	Series: mathematics, mechanics, informatics,} 9, 2, 30--37, 2009.
\item A.\,Gavryushkin.
	Spectra of computable models for Ehrenfeucht theories.
	{\em Algebra and Logic,} 46, 3, 149--157, 2007.
\item A.\,Gavryushkin.
	On complexity of Ehrenfeucht theories with computable model.
	{\em Logical Approaches to Computational Barriers---CiE,} 105--108, 2006.
\item A.\,Gavryushkin.
	Complexity of Ehrenfeucht models.
	{\em Algebra and Logic,} 45, 5, 289--295, 2006.}
{}
\end{itemize}

\iftoggle{full}{
\centerline{\bf Invited Talks}
}{
\centerline{\bf Recent invited talks}
}
\begin{tabbing}
0000000000	\= 000000 \= 00000000000000000000000000000000000000000	\= \kill
April		\> 2018 \> {\em Department of Biochemistry Seminar}	\> Seminar talk\\
		\>	\> Otago University				\> \\
July		\> 2017 \> {\em SIAM Applied Algebraic Geometry}	\> Symposium talk\\
		\>      \> {\em Polyhedral and Combinatorial Biology Symposium}\> \\
		\>      \> at Georgia Tech in Atlanta			\> \\
May		\> 2017 \> {\em Interactions between Algebra and the Sciences}\> Workshop talk\\
		\>	\> at Max Planck Institute in Leipzig		\> \\
June		\> 2016 \> {\em Evolution Meeting}			\> Spotlight session talk\\
		\>	\> in Austin, Texas				\> \\
November	\> 2015	\> {\em Computational Biology Group Seminar}	\> Seminar talk\\
		\>	\> at ETH---Zurich				\> \\
February	\> 2015	\> {\em Matsen Group Seminar}			\> Seminar talk\\
		\>	\> at Fred Hutchinson Cancer Research Centre	\> \\
February	\> 2015	\> {\em Workshop on Networks of Life}		\> Workshop talk\\
		\>	\> at the University of Canterbury		\>
\iftoggle{full}{\\
June		\> 2014	\> {\em Algebra and Mathematical Logic:}	\> Special session talk\\
		\>	\> {\em Theory and Applications} in Kazan	\> \\
November	\> 2013	\> {\em Randomness Workshop}			\> Workshop talk\\
		\>	\> at the University of Auckland		\> \\
November	\> 2012	\> National University of Singapore		\> Seminar talk\\
March		\> 2012	\> Auckland University of Technology		\> Seminar talk\\
October		\> 2011	\> {\em Maltsev Meeting} in Novosibirsk		\> Plenary talk\\
October		\> 2011	\> {\em Logic Seminar} at Cornell University	\> Seminar talk\\
September	\> 2011	\> {\em Southern Wisconsin Logic Colloquium}	\> Seminar talk\\
		\>	\> University of Wisconsin---Madison		\> \\
November	\> 2009	\> {\em Computational Logic Seminar}		\> Seminar talk\\
		\>	\> at CUNY Graduate Centre			\> \\
October		\> 2009	\> {\em Logic Seminar} at Cornell University	\> Seminar talk\\
October		\> 2009	\> {\em Logic Seminar}				\> Seminar talk\\
		\>	\> at the University of Notre Dame		\> \\
November	\> 2007	\> {\em Maltsev Meeting} in Novosibirsk		\> Plenary talk\\
September	\> 2006	\> {\em Algebra and Logic Seminar}		\> Seminar talk\\
		\>	\> at Novosibirsk State University		\> \\
June		\> 2005	\> {\em Joint Seminar on Constructive Models}	\> Seminar talk\\
		\>	\> Notre Dame and Novosibirsk Universities	\> \\
November	\> 2004	\> {\em Algebra and Logic Seminar}		\> Seminar talk\\
		\>	\> at Novosibirsk State University		\>
}{}
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Contributed Talks}
\begin{tabbing}
0000000000	\= 000000 \= 00000000000000000000000000000000000000000	\= \kill
February	\> 2016	\> {\em Computational Cancer Biology}		\> Participant\\
		\>	\> at University of California, Berkeley	\> \\
October		\> 2015	\> {\em Alan Wilson Centre Annual Meeting}	\> Long talk\\
		\>	\> at Massey University				\> \\
February	\> 2015	\> {\em The Interface of Mathematics and Biology}\> Long talk\\
		\>	\> {\em NZ Phylogenomics Meeting} in Dunedin	\> \\
February	\> 2014	\> {\em Workshop on Networks of Life}		\> Participant\\
		\>	\> at the University of Canterbury		\> \\
June		\> 2013	\> {\em Mathematical and Computational}		\> Participant\\
		\>	\> {\em Evolutionary Biology} in Montpellier	\> \\
July		\> 2013	\> {\em Computability in Europe} in Milan	\> Two contributed talks\\
July		\> 2011	\> {\em Infinity Conference} in Barcelona	\> Contributed talk\\
July		\> 2011	\> {\em Logic Colloquium} in Barcelona 		\> Contributed talk\\
July		\> 2010	\> {\em Logic Colloquium} in Paris		\> Contributed talk\\
June		\> 2010	\> {\em Computability in Europe} in Azores	\> Contributed talk\\
May		\> 2010	\> {\em Maltsev Meeting} in Novosibirsk		\> Contributed talk\\
August		\> 2009	\> {\em Logic Colloquium} in Sofia		\> Contributed talk\\
June		\> 2008	\> {\em Computability in Europe} in Athens	\> Contributed talk\\
July		\> 2007	\> {\em Logic Colloquium} in Wroclaw		\> Contributed talk\\
July		\> 2006	\> {\em Computability in Europe} in Swansea 	\> Contributed talk
\end{tabbing}
}{}

\centerline{\bf Grants}

\begin{tabbing}
00000000000	\= \kill
2018--2023	\> Principal Investigator and Coordinator of a Rutherford Discovery Fellowship\\
		\> from the Royal Society of New Zealand\\
		\> Contract \#RDF-17-UOO-007 for NZ\$\,800,000 (GST exclusive)\\
2012--2013	\> Associate Investigator of an FRDF grant from the University of Auckland\\
		\> Contract \#\,2795185 for NZ\$\,200,000\\
2011--2013	\> Principal Investigator and Coordinator of a Russian Government Grant\\
		\> Contract \#\,16.740.11.0567 for US\$\,50,000\\
2010--2012	\> Principal Investigator and Coordinator of a Russian Government Grant\\
		\> Contract \#\,$\Pi1227$ for US\$\,65,000
\iftoggle{full}{\\
2006--2010	\> Participant of a Russian Fund for Fundamental Research Grant\\
2003--2009	\> Participant of a Russian President Grant
\end{tabbing}

\newpage
\centerline{\bf Travel Grants}
\begin{tabbing}
00000000000	\= \kill
2012--2013	\> School of Computing, National University of Singapore\\
2011		\> University of Chicago, University of Wisconsin--Madison, and Cornell University\\
2011		\> Participation in the Logic Colloquium 2011\\
2010		\> Participation in the Logic Colloquium 2010\\
2010		\> Participation in the Computability in Europe 2010\\
2009		\> University of Notre Dame, Cornell University, and NYC University\\
2009		\> Participation in the Logic Colloquium 2009\\
2008		\> Participation in the Computability in Europe 2008\\
2008		\> Participation in the Summer School Marktoberdorf 2008\\
2007		\> Participation in the Logic Colloquium 2007\\
2006		\> Participation in the Computability in Europe 2006
\end{tabbing}
}{\end{tabbing}
\newpage
}

\centerline{\bf Students}

\begin{tabbing}
0000000000000	\= 000000000000000000	\= 0000000	\= 00000000000000000000000000000000000000000000000000000	\= \kill
2018--present	\> Kieran Elmes		\> Project	\> University of Otago\\
2017--present	\> Lena Collienne	\> Master	\> University of Greifswald\\
2015--2016	\> Lena Collienne	\> Intern	\> The University of Auckland (University of Greifswald)\\
2015--2016	\> Edwardo Reynolds	\> Intern	\> The University of Auckland
\end{tabbing}

\iftoggle{full}{
\centerline{\bf Teaching}
}{
\centerline{\bf Recent teaching}
}

\begin{tabbing}
00000000000	\= 0000000000000000000000000000	\= \kill
2017--2017	\> ETH Zurich			\> Systems Genomics (636-0101-00L)\\
2012--2014	\> The University of Auckland	\> Discrete Structures in Math and CS (CompSci\,225)\\
2013--2014	\> Auckland U of Technology	\> Engineering Mathematics I and II (715001/716001)\\
2013--2013	\> Auckland U of Technology	\> Finite Mathematics (715205)\\
2012--2012	\> Auckland U of Technology	\> Theory of Computation (717300)\\
2012--2012	\> The University of Auckland	\> Software Engineering Theory (SoftEng\,211)
\iftoggle{full}{\\
2010--2011	\> Irkutsk State University	\> Computable Model Theory\\
2009--2010	\> Irkutsk State University	\> Model Theory\\
2009--2011	\> Irkutsk State University	\> Mathematical Logic\\
2010--2011	\> Irkutsk State University	\> Discrete Mathematics\\
2009--2010	\> Irkutsk State University	\> Theory of Computation\\
2006--2009	\> Novosibirsk State University	\> Theory of Algorithms\\
2007--2009	\> Novosibirsk State University	\> Theoretical Programming\\
2007--2009	\> Novosibirsk State University	\> Mathematical Logic\\
2007--2008	\> Novosibirsk State University	\> Number Theory
\end{tabbing}
}{
\end{tabbing}
}

\centerline{\bf Professional Affiliation}
\begin{tabbing}
000000	\= 0000000000000000000000000000000000000000000000000000000000	\= \kill
2016	\> Society of Systematic Biologists				\> Member\\
2016	\> The Geological Society of America				\> Member
\end{tabbing}

\iftoggle{full}{\newpage}{}
\centerline{\bf Service to Department and University}
\begin{tabbing}
000000	\= 0000000000000000000000000000000000000000000000000000000000	\= \kill
2013	\> Auckland--Novosibirsk Workshop on				\> Co-Chair of the\\
	\> Algebra, Logic, Geometry, and Combinatorics			\> Program Committee\\
2009	\> Maltsev Meeting						\> Organizing Committee\\
2007	\> Mathematics in the Modern World				\> Organizing Committee\\
2007	\> Domains VIII and Computability Over Continuous Data Types	\> Organizing Committee\\
2005	\> Asian Logic Conference					\> Organizing Committee
\end{tabbing}

\noindent I am a regular reviewer for {\em AMS Mathematical Reviews}.
I recently acted as a referee for:
\medskip\\
$\bullet$ {\em Genome Biology and Evolution}\\
$\bullet$ {\em Systematic Biology}\\
$\bullet$ {\em Journal of Mathematical Biology}\\
$\bullet$ {\em Discrete Applied Mathematics}\\
$\bullet$ {\em LICS Symposium}\\
$\bullet$ {\em Algebra and Logic}
\vskip30pt
\iftoggle{full}{
\begin{tabbing}
0000000000000000000	\= 0000000000000000000000000000000000000000000	\= \kill
Up-to-date full CV:	\> \url{http://lab.gavruskin.com/alex/AGcv.pdf}\\
			\> \\
Up-to-date short CV:	\> \url{http://lab.gavruskin.com/alex/AGcv_short.pdf}
\end{tabbing}
}{
\noindent Up-to-date CV: \url{http://lab.gavruskin.com/alex/AGcv_short.pdf}
}
\end{document}
